### 2023-10-02 latex/paper/main.tex
paper inv section

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    aboveskip=15pt, % Adjust the space above the listing
    belowskip=15pt, % Adjust the space below the listing
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

@@

\pagebreak
\subsubsection{Inverse}
The \textbf{inverse of a matrix} is a fundamental concept in linear algebra. For a square matrix $A$, if an inverse exists, it is denoted as $A^{-1}$. A matrix is invertible (or non-singular) if and only if its determinant is non-zero. The concept of the inverse of a matrix is closely related to solving linear systems of equations. Consider a system of linear equations represented in matrix form as $Ax = b$: 
$$
\begin{array}{@{}cccc@{}}
    A & x &  & b \\
    \begin{bmatrix}
        a_{11} & a_{12} & \cdots & a_{1n} \\
        a_{21} & a_{22} & \cdots & a_{2n} \\
        \vdots & \vdots & \ddots & \vdots \\
        a_{m1} & a_{m2} & \cdots & a_{mn}
    \end{bmatrix}
    &
    \begin{bmatrix}
        x_1 \\
        x_2 \\
        \vdots \\
        x_n
    \end{bmatrix}
    & = &
    \begin{bmatrix}
        b_1 \\
        b_2 \\
        \vdots \\
        b_m
    \end{bmatrix}
\end{array}
$$
where:
\begin{itemize}
    \item{$A$ is the coefficient matrix}
    \item{$x$ is the vector of variables we want to solve for}
    \item{$b$ is the vector of constants on the right-hand side}
\end{itemize}
The \textbf{solution} for $x$ can be found using the inverse of $A$, hence $x = A^{-1}b$. To find the inverse of a matrix, one common method is to use the formula:
$$
    A^{-1} = \frac{1}{\det(A)} \cdot \text{adj}(A)
$$
where $\det(A)$ denotes the determinant of matrix $A$ and $\text{adj}(A)$ represents the \textbf{adjugate} of matrix $A$. The adjugate of matrix $A$ is obtained by taking the transpose of the \textbf{matrix of cofactors} of $A$. The cofactor $C_{ij}$ is calculated as:
$$
    C_{ij} = (-1)^{i+j} \cdot \det(M_{ij})
$$
where $\det(M_{ij})$ represents the determinant of the submatrix obtained by deleting the $i$th row and $j$th column from matrix $A$. The inverse of matrix $A$ satisfies the following condition:
$$
    A \cdot A^{-1} = A^{-1} \cdot A = I
$$

>>>>

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
% \definecolor{backcolour}{rgb}{0.95,0.95,0.95}
\definecolor{backcolour}{rgb}{1,1,1}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    aboveskip=15pt, % Adjust the space above the listing
    belowskip=15pt, % Adjust the space below the listing
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

@@

\pagebreak
\subsubsection{Inverse}
The \textbf{inverse of a matrix} is a fundamental concept in linear algebra. For a square matrix $A$, if an inverse exists, it is denoted as $A^{-1}$. A matrix is invertible (or non-singular) if and only if its determinant is non-zero. The concept of the inverse of a matrix is closely related to solving linear systems of equations. Consider a system of linear equations represented in matrix form as $Ax = b$: 
$$
\begin{array}{@{}cccc@{}}
    A & x &  & b \\
    \begin{bmatrix}
        a_{11} & a_{12} & \cdots & a_{1n} \\
        a_{21} & a_{22} & \cdots & a_{2n} \\
        \vdots & \vdots & \ddots & \vdots \\
        a_{m1} & a_{m2} & \cdots & a_{mn}
    \end{bmatrix}
    &
    \begin{bmatrix}
        x_1 \\
        x_2 \\
        \vdots \\
        x_n
    \end{bmatrix}
    & = &
    \begin{bmatrix}
        b_1 \\
        b_2 \\
        \vdots \\
        b_m
    \end{bmatrix}
\end{array}
$$
where:
\begin{itemize}
    \item{$A$ is the coefficient matrix}
    \item{$x$ is the vector of variables we want to solve for}
    \item{$b$ is the vector of constants on the right-hand side}
\end{itemize}
The \textbf{solution} for $x$ can be found using the inverse of $A$, hence $x = A^{-1}b$. To find the inverse of a matrix, one common method is to use the formula:
$$
    A^{-1} = \frac{1}{\det(A)} \cdot \text{adj}(A)
$$
where $\det(A)$ denotes the determinant of matrix $A$ and $\text{adj}(A)$ represents the \textbf{adjugate} of matrix $A$. The adjugate of matrix $A$ is obtained by taking the transpose of the \textbf{matrix of cofactors} of $A$. The cofactor $C_{ij}$ is calculated as:
$$
    C_{ij} = (-1)^{i+j} \cdot \det(M_{ij})
$$
where $\det(M_{ij})$ represents the determinant of the submatrix obtained by deleting the $i$th row and $j$th column from matrix $A$. The inverse of matrix $A$ satisfies the following condition:
$$
    A \cdot A^{-1} = A^{-1} \cdot A = I
$$
\pagebreak
\\
We write the algorithm in Python as the following:
\begin{lstlisting}[language=Python, label={Inverse function}]
def inv(self):
    if not self.is_square():
        raise Exception("Matrix must be square")

    elif self.det() == 0:
        raise Exception("Matrix is not invertible")

    else:
        rows, cols = self.shape()
        data = self.get()

        det = self.det()

        # special case for 2x2 matrix:
        if rows == cols == 2:
            return [[data[1][1] / det, -1 * data[0][1] / det],
                    [-1 * data[1][0] / det, data[0][0] / det]]

        # find matrix of cofactors
        cof_matrix = []

        for row in range(rows):
            cof_row = []

            for column in range(cols):
                minor = self.minor(row, column)

                cof_row.append(((-1)**(row + column)) * minor.det())

            cof_matrix.append(cof_row)

        cof_matrix = Matrix(cof_matrix).transpose()

        cof_rows, cof_cols = cof_matrix.shape()
        cof_data = cof_matrix.get()

        for row in range(cof_rows):
            for column in range(cof_cols):
                cof_data[row][column] = cof_data[row][column] / det

        return cof_matrix
\end{lstlisting}
To parallelize this function, we make use of the previously parallelized function \textit{det}, and define the new auxiliary functions \textit{inv\_cof\_matrix} and \textit{inv\_calc}:

\begin{lstlisting}[language=Python, caption={inv\_calc}]
    @ray.remote
    def inv_calc(row, cof_cols, cof_data, det):
        for col in range(cof_cols):
            return (row, col, (cof_data[row][col] / det))
    \end{lstlisting}
\pagebreak
\begin{lstlisting}[language=Python, caption={inv\_cof\_matrix}]
@ray.remote
def inv_cof_matrix(A, row, cols):

    cof_row = []

    for column in range(cols):
        minor = A.minor(row, column)
        cof_row.append(((-1)**(row + column)) * minor.det())

    return cof_row
\end{lstlisting}
\begin{lstlisting}[language=Python, caption={Parallelized inverse function}]
def inv(self):
    if not self.is_square():
        raise Exception("Matrix must be square")

    elif self.det() == 0:
        raise Exception("Matrix is not invertible")

    else:
        rows, cols = self.shape()
        data = self.get()
        det = self.det()

        # special case for 2x2 matrix:
        if rows == cols == 2:
            m = [[data[1][1] / det, -1 * data[0][1] / det],
                    [-1 * data[1][0] / det, data[0][0] / det]]

            return Matrix([[round(i, 8) for i in j] for j in m])

        # find matrix of cofactors
        cof_rows_futures = [t.inv_cof_matrix.remote(self, row, cols) 
                                for row in range(rows)]

        cof_matrix = ray.get(cof_rows_futures)
        cof_matrix = Matrix(cof_matrix).transpose()

        cof_rows, cof_cols = cof_matrix.shape()
        cof_data = cof_matrix.get()

        data_futures = [t.inv_calc.remote(row, cof_cols, cof_data, det) 
                            for row in range(cof_rows)]

        for data in ray.get(data_futures):
            for row, col, value in [data]:
                cof_data[row][col] = value

        return Matrix([[round(i, 8) for i in j] for j in cof_matrix])
\end{lstlisting}
